Enter our title here

### 2017-09-10 manuscript.tex
added question

@@

With this increased use of R in classrooms, there is a need for an effective way to get students familiar with statistical software
\cite{Baumer2014}. While Rsoftware provides users with extraordinary abilities there is no doubt a steep learning curve. To facilitate
this transition to R programming, popular interactive teaching technologies have been created including Swirl (need to cite this?), LearnR
and TryR. 
These tools allow students to work through coding problems while recieving immediate feedback in and out of the classroom. Swirl is an
open source R software package that allows students to learn R programing in their R console. This interactive learning tool
contains several pre-existing lessons but what makes Swirl so popular is its versitality; educators can create their own
lesson (or tailor a pre-existing one) to fit their curriculum and assign it to students \cite{Carchedi2014}.
While swirl can be linked to a Massive Open Online Courses (MOOCs) like Coursera through API, integration of learning management 
systems (LMS) is not available for the classroom.

@@

TryR (Code School 2014) is a web-based programs and does not have this reproducible capability. Since public content authoring
is not available, educators are limited on what they can teach their students. The R console can be intimidating to
introductory statistics students so an advantage of a web-based teaching tool is
the clean and easy to use interface. This is an important quality given that a lot of the time students struggle more with
software than the statistical concepts themselves \cite{Hare2017}. When students only need their web browser to participate,
all installation complications are avoided and valuable class time can be focused on the statistics, not computer issues.

DataCamp has the same reproducable capabilities as Swirl but is a web-based application; educators can
create their own courses that coincide with their lessons and students can access the course without having to install R.
Courses are available through the DataCamp website and students can access the lesson through their web-browser on a laptop,
tablet or moble device, making the courses accessable to anyone with an internet connection. 
The DataCamp website offers pre-existing free community courses as well as specialized 'Premium' classes that you need to purchase. 
However, when used for academic purposes the premium DataCamp content is also free of charge.. (i'll come back to this).
Any college educator can create a classroom group on the DataCamp website, add student's to the group, assign pre-existing 
'community' courses or assign a course that they've created for the particular class.

>>>>

5) should i add that the courses are written in Hadley Wickham style?

@@

With this increased use of R in classrooms, there is a need for an effective way to get students familiar with statistical software
\cite{Baumer2014}. While Rsoftware provides users with extraordinary abilities there is no doubt a steep learning curve. To facilitate
this transition to R programming, popular interactive teaching technologies have been created including Swirl (**need to cite this?
if so what should i cite**), LearnR and TryR. 
These tools allow students to work through coding problems while recieving immediate feedback in and out of the classroom. Swirl is an
open source R software package that allows students to learn R programing in their R console. This interactive learning tool
contains several pre-existing lessons but what makes Swirl so popular is its versitality; educators can create their own
lesson (or tailor a pre-existing one) to fit their curriculum and assign it to students \cite{Carchedi2014}.
While swirl can be linked to a Massive Open Online Courses (MOOCs) like Coursera through API, integration of learning management 
systems (LMS) is not available for the classroom.

@@

Try R website --> \url{http://tryr.codeschool.com} i dont know how to cite this with mendeley
TryR (Code School 2014) is a web-based programs and does not have this reproducible capability. Since public content authoring
is not available, educators are limited on what they can teach their students. The R console can be intimidating to
introductory statistics students so an advantage of a web-based teaching tool is
the clean and easy to use interface. This is an important quality given that a lot of the time students struggle more with
software than the statistical concepts themselves \cite{Hare2017}. When students only need their web browser to participate,
all installation complications are avoided and valuable class time can be focused on the statistics, not computer issues.

The purpose of this paper is to introduce a relatively new interactive teaching tool, DataCamp, which incorporates only the best
qualities from the tools mentioned above.

DataCamp has the same reproducable capabilities as swirl but is a web-based application; educators can
create their own courses that coincide with their lessons and students can access the course without having to install R.
Courses are available through the DataCamp website and students can access the lesson through their web-browser on a laptop,
tablet or moble device, making the courses accessable to anyone with an internet connection. 
The DataCamp website offers pre-existing free community courses as well as specialized 'Premium' classes that you need to purchase. 
However, when used for academic purposes the premium DataCamp content is also free of charge.. (i'll come back to this).
Any college educator can create a classroom group on the DataCamp website, add student's to the group, assign pre-existing 
'community' courses or assign a course that they've created for the particular class.
